Elders stove grades and usage summary

### 2022-01-28 letter_results.Rmd
Update figures for NPT community results presentation

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) %>% 
  mutate(cohort = factor(cohort, levels = c("2015", "2016", "2017", "2018", "2019"))) %>% 
  filter(area == "NPT") %>% 
  #filter(pm_mean_winter < 200) %>% 
  mutate("Winter:" = factor(winter_id, levels = c(1, 2),
                                  labels = c("1st Winter/Pre-Intervention", "2nd Winter/Post-Intervention")),
         treatment = factor(treatment, 
                            levels = c("Placebo", "Education", "Filter"),
                            labels = c("Placebo Group", "Education Group", "Filter Group")),
         pm_mean_winter = round(pm_mean_winter, digits = 0),
         mp_mean_winter = round(mp_mean_winter, digits = 0))

@@

![](npt_logo.png)

## Your Nimiipuu EldersAIR Study Results  
Your results may be different from other participants' results depending on 1) how often and/or how efficiently you used your stove and 2) your study group and how consistently you used the education or air filter interventions. See the **Overview** for a detailed description of the three study groups and other frequently asked questions.

## Reading Your Results  
**Graph:** The triangles in the graph show 1) your study results and 2) which study group you were in. Next to each triangle is the numerical value for each measurement. The small circles represent the other Nimiipuu participant results.

@@

### Air Pollution Results
Wood smoke is made up of a complex mixture of gases and particles. The biggest health threat from smoke is from fine particles or PM2.5. PM2.5 is measured in micrograms per cubic meter (ug/m3) of air. For this project, the PM2.5 number is an average of four days (two, 48-hour samples) each winter.  
There are no health-based guidelines for indoor PM2.5. However, for outdoor air the U.S. Environmental Protection Agency recommends that communities not exceed an average concentration of 35 µg/m3 during a 24-hour period (this is the dotted RED line on the Air Pollution graphs).

@@

#### Indoor PM2.5  
We measured indoor PM2.5 using the stationary, DustTrak monitor near your wood stove.  
```{r, fig.height = 3.5, fig.width = 8}
indoor_pm_plot <- analysis_data %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  filter(!is.na(treatment)) %>% 
  distinct(home, winter_id, .keep_all = T) %>% 
  ggplot() + 
    #geom_boxplot(aes(treatment, pm_mean_winter, fill = `Winter:`, size = 1), 
     #            lwd = 1.2, colour = "black", 
      #           fatten = 1, outlier.size = 1.5, width = 0.35) +
    geom_hline(yintercept = 35, color = "red", linetype = 2) + 
    geom_point(aes(treatment, pm_mean_winter, fill = `Winter:`), 
               shape = 21, size = 3, position=position_jitterdodge(seed = 1)) +
    geom_label(aes(treatment, pm_mean_winter, label = pm_mean_winter, 
                   color = `Winter:`), 
               data = data_pm, size = 5, position=position_dodge(1.6)) +
    geom_point(aes(treatment, pm_mean_winter, fill = `Winter:`), 
               data = data_pm, shape = 24, size = 4, stroke = 3, 
               position=position_dodge(0.9)) +
    labs(y = "Indoor PM2.5", fill = "", color = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) 
indoor_pm_plot
```

#### Personal PM2.5  
We measured personal PM2.5 using the portable, MicroPem monitor in the small pouch.  
```{r}
personal_pm_plot <- analysis_data %>% 
  filter(!is.na(mp_mean_winter)) %>% 
  filter(!is.na(treatment)) %>% 
  distinct(home, winter_id, .keep_all = T) %>% 
  ggplot() + 
    geom_hline(yintercept = 35, color = "red", linetype = 2) + 
    geom_point(aes(treatment, mp_mean_winter, fill = `Winter:`), 
               shape = 21, size = 3, position=position_jitterdodge(seed = 1)) +
    geom_label(aes(treatment, mp_mean_winter, label = mp_mean_winter, 
                   color = `Winter:`), 
               data = data_mp, size = 5, position=position_dodge(1.6)) +
    geom_point(aes(treatment, mp_mean_winter, fill = `Winter:`), 
               data = data_mp, shape = 24, size = 4, stroke = 3, 
               position=position_dodge(0.9)) +
    labs(y = "Personal PM2.5", fill = "", color = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) 
personal_pm_plot
```

### Health Results

>>>>

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) %>% 
  mutate(cohort = factor(cohort, levels = c("2015", "2016", "2017", "2018", "2019"))) %>% 
  filter(area == "NPT") %>% 
  #filter(pm_mean_winter < 200) %>% 
  #filter(home == "NPE5301") %>% 
  mutate("Winter:" = factor(winter_id, levels = c(1, 2),
                                  labels = c("1st Winter/Pre-Intervention", "2nd Winter/Post-Intervention")),
         treatment = factor(treatment, 
                            levels = c("Placebo", "Education", "Filter"),
                            labels = c("Placebo Group", "Education Group", "Filter Group")),
         pm_mean_winter = round(pm_mean_winter, digits = 0),
         mp_mean_winter = round(mp_mean_winter, digits = 0))

@@

![](npt_logo2.png)

### Your Nimiipuu EldersAIR Study Results  
Your results may be different from other participants' results depending on 1) how often and/or how efficiently you used your stove and 2) your study group and how consistently you used the education or air filter interventions. See the **Overview** for a detailed description of the three study groups and other frequently asked questions related to your results.

**Graph:** The triangles in the graph show 1) your study results and 2) which study group you were in. Next to each triangle is the numerical value for each measurement. The small circles represent the other Nimiipuu participant results.

@@

#### Indoor PM2.5 Air Pollution  
We measured indoor PM2.5 using the stationary DustTrak monitor near your wood stove.  
```{r, fig.height = 2.5, fig.width = 8}
indoor_pm_plot <- analysis_data %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  filter(!is.na(treatment)) %>% 
  distinct(home, winter_id, .keep_all = T) %>% 
  ggplot() + 
    #geom_boxplot(aes(treatment, pm_mean_winter, fill = `Winter:`, size = 1), 
     #            lwd = 1.2, colour = "black", 
      #           fatten = 1, outlier.size = 1.5, width = 0.35) +
    #geom_hline(yintercept = 35, color = "red", linetype = 2) + 
    geom_point(aes(treatment, pm_mean_winter, fill = `Winter:`), 
               shape = 21, size = 3, position=position_jitterdodge(seed = 1)) +
    geom_label(aes(treatment, pm_mean_winter, label = pm_mean_winter, 
                   color = `Winter:`), 
               data = data_pm, size = 5, position=position_dodge(1.6)) +
    geom_point(aes(treatment, pm_mean_winter, fill = `Winter:`), 
               data = data_pm, shape = 24, size = 4, stroke = 3, 
               position=position_dodge(0.9)) +
    labs(y = "Indoor PM2.5", fill = "", color = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) 
indoor_pm_plot
```

#### Personal PM2.5 Air Pollution  
We measured personal PM2.5 using the portable MicroPem monitor in the small pouch.  
```{r, fig.height = 2.5, fig.width = 8}
personal_pm_plot <- analysis_data %>% 
  filter(!is.na(mp_mean_winter)) %>% 
  filter(!is.na(treatment)) %>% 
  distinct(home, winter_id, .keep_all = T) %>% 
  ggplot() + 
    #geom_hline(yintercept = 35, color = "red", linetype = 2) + 
    geom_point(aes(treatment, mp_mean_winter, fill = `Winter:`), 
               shape = 21, size = 3, position=position_jitterdodge(seed = 1)) +
    geom_label(aes(treatment, mp_mean_winter, label = mp_mean_winter, 
                   color = `Winter:`), 
               data = data_mp, size = 5, position=position_dodge(1.6)) +
    geom_point(aes(treatment, mp_mean_winter, fill = `Winter:`), 
               data = data_mp, shape = 24, size = 4, stroke = 3, 
               position=position_dodge(0.9)) +
    labs(y = "Personal PM2.5", fill = "", color = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) 
personal_pm_plot
```

@@

### 2022-01-28 main_analysis_final.Rmd
Update figures for NPT community results presentation

# Exposure-response analysis
```{r}
## select outcome variable
### bp_sys, bp_dia, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp, pm_mean_visit
er_data_4row <- analysis_data %>% 
  #filter(spiro_status == "Acceptable") %>%  # only use this filter for spiro outcomes
  mutate(outcome = bp_dia) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, pm_mean_visit,
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff, 
                pm_mean_at_home_visit, mp_mean_visit,
                treatment_filter_type, filter_compliance, kw_perc_expected) %>% 
  mutate(pm_iqr = pm_mean_visit/32,
         pm_at_home_iqr = pm_mean_at_home_visit/32) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T)

@@

summary(er_results_primary)

>>>>

# Exposure-response analysis
```{r}
## select outcome variable
### bp_sys, bp_dia, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp, pm_mean_visit
er_data_4row <- analysis_data %>% 
  #filter(spiro_status == "Acceptable") %>%  # only use this filter for spiro outcomes
  mutate(outcome = bp_sys) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, pm_mean_visit,
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff, 
                pm_mean_at_home_visit, mp_mean_visit,
                treatment_filter_type, filter_compliance, kw_perc_expected) %>% 
  mutate(pm_iqr = pm_mean_visit/32,
         pm_at_home_iqr = pm_mean_at_home_visit/32) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T)

@@

#summary(er_results_primary)

### 2022-01-28 main_analysis_pm.Rmd
Update figures for NPT community results presentation

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) %>% 
  mutate(cohort = factor(cohort, levels = c("2015", "2016", "2017", "2018", "2019")))

@@

# Indoor/Area PM2.5
```{r}
# Prep data for primary analysis - 1 row per winter
pm_data_2row <- analysis_data %>%
  #filter(area == "NN") %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level, moisture_ave, sums_winter_mean,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

# Prep data for sensitivity analysis - at-home PM data
pm_at_home_data <- analysis_data %>% 
  mutate(outcome = pm_mean_at_home_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level, moisture_ave,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

>>>>

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) %>% 
  mutate(cohort = factor(cohort, levels = c("2015", "2016", "2017", "2018", "2019"))) 
#  select(home, mp_mean_winter, pm_mean_winter) %>% 
#  arrange(desc(mp_mean_winter))
#head(analysis_data)

@@

# Indoor/Area PM2.5
```{r}
# Prep data for primary analysis - 1 row per winter
pm_data_2row <- analysis_data %>%
  #filter(area == "NN") %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level, moisture_ave, sums_winter_mean,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  #filter(home != "NPE5301") %>% 
  ungroup()

# Prep data for sensitivity analysis - at-home PM data
pm_at_home_data <- analysis_data %>% 
  mutate(outcome = pm_mean_at_home_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level, moisture_ave,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  #filter(home != "NPE5301") %>% 
  ungroup()

@@

# Boxplot figure for results letter
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")

indoor_pm_boxplot <- analysis_data %>% 
  filter(area == "NPT") %>% 
  mutate("Winter:" = factor(winter_id, levels = c(1, 2),
                                  labels = c("1st Winter/Pre-Intervention", "2nd Winter/Post-Intervention")),
         treatment = factor(treatment, 
                            levels = c("Placebo", "Education", "Filter"),
                            labels = c("Placebo Group", "Education Group", "Filter Group"))) %>% 
  filter(!is.na(pm_mean_visit)) %>% 
  filter(pm_mean_visit < 200) %>% 
  filter(!is.na(treatment)) %>% 
  ggplot(aes(treatment, pm_mean_visit, fill = `Winter:`)) + 
    geom_boxplot(aes(treatment, pm_mean_visit, fill = `Winter:`, size = 1), 
                 lwd = 1.2, colour = "black", 
                 fatten = 1, outlier.size = 1.5, width = 0.35,
                 outlier.shape = NA) +
    #stat_summary(fun.y=mean, geom="point", shape = 3, size = 3, stroke = 2, 
     #          position=position_dodge(0.35)) +
    labs(y = expression(paste("Indoor PM"[2.5], " (", mu, g/m^3, ")")),
         fill = "") +
    theme_minimal() +
    scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10), limits = c(0, 130)) +
    #scale_y_log10() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9"))
indoor_pm_boxplot

indoor_pm_plot <- analysis_data %>% 
  filter(area == "NPT") %>% 
  filter(pm_mean_visit < 200) %>% 
  mutate("Winter:" = factor(winter_id, levels = c(1, 2),
                                  labels = c("1st Winter/Pre-Intervention", "2nd Winter/Post-Intervention")),
         treatment = factor(treatment, 
                            levels = c("Placebo", "Education", "Filter"),
                            labels = c("Placebo Group", "Education Group", "Filter Group"))) %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  filter(!is.na(treatment)) %>% 
  distinct(home, winter_id, .keep_all = T) %>% 
  ggplot() + 
    #geom_hline(yintercept = 35, color = "red", linetype = 2) + 
    geom_point(aes(treatment, pm_mean_winter, fill = `Winter:`), 
               shape = 21, size = 3, position=position_jitterdodge(seed = 1)) +
    labs(y = "Indoor PM2.5", fill = "", color = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) 
indoor_pm_plot

#ggsave("elders_pm_dotplots.jpg", width = 8, height = 5)
```

### 2022-01-28 manuscript_tables_figures.Rmd
Update figures for NPT community results presentation

>>>>

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")

stove_grade_plot <- elders_cleaned_dataset_by_visit %>% 
  filter(area == "NPT") %>% 
  select(home, winter_id, stove_grade) %>% 
  arrange(home, stove_grade) %>% 
  distinct(home, .keep_all = T) %>% 
  filter(!is.na(stove_grade)) %>% 
  mutate(stove_grade_new = factor(stove_grade,
                                  levels = c("A", "C", "F"),
                                  labels = c("High-quality",
                                             "Medium-quality",
                                             "Low-quality"))) %>% 
  ggplot() +
    geom_bar(aes(stove_grade_new, fill = stove_grade_new)) +
    labs(y = "", fill = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"))
stove_grade_plot

#ggsave("elders_stove_grade_plot.jpg", width = 6, height = 6)

stove_age_plot <- elders_cleaned_dataset_by_visit %>% 
  filter(area == "NPT") %>% 
  select(home, winter_id, stove_age) %>% 
  arrange(home, stove_age) %>% 
  distinct(home, .keep_all = T) %>% 
  filter(!is.na(stove_age)) %>% 
  ggplot() +
    geom_bar(aes(stove_age, fill = stove_age)) +
    labs(y = "", fill = "") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          legend.title = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid.major.x = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_manual(values = cbPalette)
stove_age_plot

#ggsave("elders_stove_age_plot.jpg", width = 8, height = 6)
```

### 2022-01-28 stove_grade_usage_summary.Rmd
Update figures for NPT community results presentation

stove_use_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

>>>>

stove_use_plot <- data %>% 
  #filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
stove_use_plot
